Computational tools for representation theory of affine Lie algebras

### 2009-05-25 AffineLieAlgebras/ACMS2009/article.tex
Some textwork on folding, nothing really useful

Kac-Peterson formula is less efficient and is not discussed here.

@@

>>>>

@@

\subsection{Folding}
\label{sec:folding}

To facilitate computation of branching coefficients we can use the
idea similar to one used for computation of weight multiplicities.
There we were able to fold the star so that all the recurrent
computation took place in main Weyl chamber.

We use the formula (\ref{eq:2}). The summation in the first term of
right-hand side goes through the set of weights $\{\xi+\pi-\omega
\rho\;|\;\omega\in W\backslash e\}$
